---
title: "User Guide for SELR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User Guide for SELR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(SELR)
```

## overview
SELR package is written to implement two types of estimators based on:  
`simultaneous logistic regression` and `efficient logistic regression`. 
Designing for ordinal data, they are highly efficient for cumulative odds and 
adjacent odds and efficient for continuation ratio. By extending individualized 
logistic regression, the models could be viewed as a set of logistic regressions 
at different levels. Different binary comparisons are controlled by using 
different `risk` and `target` sets. SELR package extends `geeglm` from `geepack` 
package. For more information about `geeglm`, please see `geepack` documentation. 


## how does selr preprocess data?
SELR preprocess data by repeating input data set by `S-1` times and assigning `weights`,
`levmod`, and 0 or 1 responses for each level. Preprocess data could be viewed
in `selr` returned model values, and the original input data could be viewed in
`data` value.


## about standard models
Except the commonly used three ordinal models: cumulative, sequential, adjacent, 
baseline, and continuation ratio models, two item response theory models: two level, 
and binary splits models are implemented in `selr`. Two level model specifies
$P(Y\geq2|x)=P(Y\geq{k/2+1}|x)=F(\beta_0+x^T\beta)$ where $S_1=\{1,...,k/2\}$ and
$S_2=\{k/2+1,...,k\}$. Binary splits model specifies $P(Y\in{S_1}|Y\in{S})$ and
$P(Y\in{S_2}|Y\in{S})$ for each binary split step. 


## about `risk`, `target`, and `Z`
SELR algorithm requires either `risk` and `target` or `Z` to be assigned. To use
the argument properly, please ensure the order of levels of response data matches
with the order of `risk`, `target`, and `Z`.

## setting `elr = TRUE`
Since ELR is using "unstructured" correlation structure in `geeglm`, it should 
be used with more consideration. For more information, please see `geeglm`.


## setting `ordinal = FALSE`
Although the models are designed for ordinal data, they can be used when comparing
nominal data. SELR will force to assign the `y` argument to match the level of
response with `risk` and `target` sets for binary comparisons. 


## reference
Fu, L., & Simpson, D. G. (2002). Conditional risk models for ordinal response data:
simultaneous logistic regression analysis and generalized score tests.
Journal of Statistical Planning and Inference, 108(1–2), 201–217.
https://doi.org/10.1016/s0378-3758(02)00279-3

Tutz, G. (2021). Ordinal regression: A review and a taxonomy of models. Wiley Interdisciplinary Reviews: Computational Statistics, 14(2). https://doi.org/10.1002/wics.1545



